---
title: "Lab 00 - Hello IDS!"
author: "Xuanjie Lin"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Saba Sitter", "Emma Crawford", "Xuanjie Lin", 
           "Haoran Jiang"),
  github_username = c("sabasitter", "EmmaSC05", "xuanj315", 
                      "jimmywww"), 
  colour = c("red", "blue", "black", 
             "blue"),
  hobby = c("running", "violin", "gaming", 
            "gaming"),
  favourite_number = c(7, 3, 2, 4)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


Shows our github usernames, each of our favourite numbers, and our favourite colours.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Usernames", 
          y = "Favourite number",
          title = "Group info")
```

Modify axis, legend, and plot labels

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

Sort the hobbies into categories. e.g. exercise, music, indoors, etc. Also, using a pie chart would give a better visual representation.
